Waving and swaying

### 2013-12-18 Paper/grass.tex
Model

\section{The model}
We use a mean field average model for the coupling between the flow and the canopy. Drag force exerted by grass is approximated via continuous drag field 
which is incorporated as an additional body force $\mathbf{f}=-N\mathbf{f_d}$ in fluid momentum equation. 
%We propose a fully coupled model in order to comprehend dynamics of canopy and fluid flow, drag force excerted by grasses is
%taken as an additional body force in momentum equation of fluid. We approximate presence of grass via continuous field whose shape at any location is approximated as averaged 
%shape of grass at that location which can be obtained by assuming grass to be in quasi-equilibrium at any moment.
% and solving force balance and momentum balance for grass  
\begin{equation}
\rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad P+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}
\end{equation}
%\begin{equation}
% \mathbf{f}=-N\mathbf{f_{d}}
%\end{equation}
where $\mathbf{f_{d}}$ is drag force per unit length of grass; N is grass number density. Drag force exerted by fluid on grass depends on
fluid density $\rho$, flow velocity $\bu$, which we model as $\mathbf{f_{d}}=C_N \rho\bu_{N}^{2}d\hat{n}+C_{T}\rho\bu_{T}^{2}d\hat{t}$ where 
$C_{N}$ and $C_{T}$ are normal and tangential drag coefficients respectively; $\bu_{T}$, $\bu_{N}$ are velocity vector along and normal to grass.
%\begin{equation}
% \mathbf{f_{d}}=C_N \rho\bu_{N}^{2}d\hat{n}+C_{T}\rho\bu_{T}^{2}d\hat{t}
%\end{equation}\

>>>>

\section{The model}
We use a mean field model for the coupling between the flow and the canopy. Assuming strong oscillation in fluid flow is caused by instability of flow
composed of regions experiencing higher drag with in grass and less outside while monami being response of flexible grass to oscillations of fluid flow. We expect stiffness 
of grass to play minor role in development of flow instability. We approximate grasses with stiff cylindrical rod of diameter $d$ and height $h$ with number density $N/m^2$. 
Drag force exerted by the grass is approximated via a continuous body force $\mathbf{f}=-N\mathbf{f_d}$ in the fluid momentum balance as
%We propose a fully coupled model in order to comprehend dynamics of canopy and fluid flow, drag force excerted by grasses is
%taken as an additional body force in momentum equation of fluid. We approximate presence of grass via continuous field whose shape at any location is approximated as averaged 
%shape of grass at that location which can be obtained by assuming grass to be in quasi-equilibrium at any moment.
% and solving force balance and momentum balance for grass  
\begin{equation}
\rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad P+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}
\end{equation}
%\begin{equation}
% \mathbf{f}=-N\mathbf{f_{d}}
%\end{equation}
where $\mathbf{f_{d}}$ is drag force per unit length of grass, $\rho$ the fluid density, $\mathbf{u}$ the velocity, $P$ the pressure, $\mu$ the viscosity and $\mathbf{g}$
the acceleration due to gravity. Drag force itself is modeled as $\mathbf{f_{d}}=C_N \rho\bu_{N}^{2}d\hat{n}+C_{T}\rho\bu_{T}^{2}d\hat{t}$ where 
$C_{N}$ and $C_{T}$ are normal and tangential drag coefficients respectively which are set to zero outside the grass; $\bu_{T}$, $\bu_{N}$ are velocity vector along and
normal to grass while $\hat{t},\hat{n}$ being unit vector along and normal to grass. We expect $C_T \ll C_N$ and take $C_T=0$ for rest of analysis. We further expect $C_N$ to
not change along the height of the grass and take $C_N$ to be constant for further analysis. 
%\begin{equation}
% \mathbf{f_{d}}=C_N \rho\bu_{N}^{2}d\hat{n}+C_{T}\rho\bu_{T}^{2}d\hat{t}
%\end{equation}\
